Numerical simulation of bubble deformation \\ and breakup under simple linear shear flows

### 2024-03-31 Reply-Reviewer2.tex

%%5
\par\noindent
\item
\textsf
{Page 4: Eq. (7a) determines the evolution of F, but the need to introduce F in
addition to the colour function required by VOF (which is determined by eq.
(7b)) is not discussed. F was not even mentioned before eq. (7). The authors
should also reference previous works where the need for this distinction has
been explained.}
\vspace{3 mm}

Response: \\
We agree with reviewer's comment. We have added details of the CLSVOF method at
the beginning of Section ``A. Numerical method and governing equations.''
\\

%%6
\par\noindent
\item
\textsf
{Page 5: ``The results shown in Figure 2 verify that our numerical approach can
reproduce the same drop breakup behavior presented in [8].'' The comparison is
only qualitative, not quantitative. One can readily see several differences in
all three cases presented.  The comparison could be improved either by
superimposing the plots or even better by extracting numerical values for the
velocity field or the drop shape. The latter may be more involved, which makes
addressing issue \#7 below even more important.}
\vspace{3 mm}

Response: \\
We agree that there are ``small'' differences between the previous
study by Renardy and Cristini [8] and our present study.  We claim
that the major cause of the differences is that Renardy and
Cristini [8] used a grid size of 
$\Delta x=R/8$ 
whereas in our case,
the effective fine grid resolution had a grid size of 
$\Delta x=R/16$.  We have made this more clear in the Figure 2 caption. 
\par\noindent
Also we have made quantitative comparisons for the Taylor deformation
parameter $D$ in Table I (drop deformation) and our newly added Table II 
(bubble deformation).  Note that it took 8 months to compute the results
reported in our newly added Table II.  
Comparisons of our results
against past studies 
(summarized in Tables I and II)
support the
validity of our bubble (and drop) deformation computations.
\\

### 2024-03-31 Reply-Reviewer2.tex

%%5
\par\noindent
\item
\textsf
{Page 4: Eq. (7a) determines the evolution of F, but the need to introduce F in
addition to the colour function required by VOF (which is determined by eq.
(7b)) is not discussed. F was not even mentioned before eq. (7). The authors
should also reference previous works where the need for this distinction has
been explained.}
\vspace{3 mm}

Response: \\
We agree with reviewer's comment. We have added details of the CLSVOF method at
the beginning of Section ``A. Numerical method and governing equations.''
\\

%%6
\par\noindent
\item
\textsf
{Page 5: ``The results shown in Figure 2 verify that our numerical approach can
reproduce the same drop breakup behavior presented in [8].'' The comparison is
only qualitative, not quantitative. One can readily see several differences in
all three cases presented.  The comparison could be improved either by
superimposing the plots or even better by extracting numerical values for the
velocity field or the drop shape. The latter may be more involved, which makes
addressing issue \#7 below even more important.}
\vspace{3 mm}

Response: \\
We agree that there are several differences between the previous
study by Renardy and Cristini [8] and our present study.  We claim
that the major cause of the differences is that Renardy and
Cristini [8] used a grid size of 
$\Delta x=R/8$ 
whereas in our case,
the effective fine grid resolution had a grid size of 
$\Delta x=R/16$.  We have made this more clear in the Figure 2 caption. 
\par\noindent
We have made {\em quantitative} comparisons for the Taylor deformation
parameter $D$ in Table I (drop deformation).  In the revision, we have
added another table with {\em quantitative} comparisons.  Please
refer to our newly added Table II 
(bubble deformation).  Note that it took 8 months to compute the results
reported in our new Table II.  
Comparisons of our results
against past studies 
(summarized in Tables I and II)
support the
validity of our bubble (and drop) deformation computations.
\\

### 2024-03-31 Bubble-deformation.tex
cited Zhang et al, put in the explanation, getting close

In this work we focus on identifying critical flow states numerically, in terms
of dimensionless quantities, that specify the extreme conditions at which a
bubble or drop in shear flow first transitions from deformation to breakup.
We validate our numerical method through comparisons with previous
shear-driven drop dynamics results and we also examine the effect of drop
deformation and breakup sensitivity on domain and grid size.  An advantage of
studying shear-driven bubble deformation and breakup computationally, rather
than experimentally, is that we can easily modify fluid physical properties to
ascertain the sensitivity of deformation and breakup to physical parameters.
In our computations, the time-evolution of the boundary between gas and liquid
is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.  
We focus on determining critical physical
conditions in which the breakup of a bubble occurs in shear flow because it is
important to identify the parameter regimes in which a relatively simple system
transitions from stable to unstable.  Specifically, we identify the critical
Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
a function of $Ca$. 
The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
reported previously by \cite{LiRenRen00}.
{\color{red} In previous studies on the motion of bubble deformation
in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble defomation under very low 
$Re$ number conditions ({\color{blue} $Re \ll 1$}) have been reported.}
%{\color{blue} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
In this work we determine, for the first time, the critical Reynolds number ({\color{blue} $Re \gg 1$}) 
that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
distinguish the deformation and breakup processes of a drop versus those of a bubble.

@@

When comparing with previous drop studies, we fix $\lambda=1$.  As a result,
(for $\lambda=1$) the following dimensionless physical parameters are used to
describe the problem of drop deformation/breakup in shear flow
%
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{\rm {\color{red}m}}UR}{\mu_{\rm {\color{red}m}}}, \quad
  Ca = \frac{\mu_{\rm {\color{red}m}}U}{\sigma}, \quad
  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}}
\end{eqnarray}
%
$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
problem of shear-induced drop deformation and breakup, the velocity is set to
$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
mentioned in the introduction, most previous drop studies set $\eta =
1$ (e.g. \cite{LiRenRen00}).  
Thus, for comparison with previous drop deformation and breakup
problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
so that $g=0$). On the other hand, in our computations for bubble deformation,
we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$
and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize
that for consistency with previous studies (\cite{LiRenRen00, RusMan02,
MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
%{\color{blue} cite some of these previous studies which examine deformation
%and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
we computationally examine the deformation and breakup of a bubble in simple
linear shear flow as a function of the $Re$ and $Ca$ numbers.  {\color{red}
That is to say, by setting $g=0$, we are isolating the effect of only varying
$Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we
determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$
corresponds to the threshold of bubble (or drop) breakup.  We determine the
critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density
ratio and viscosity ratio. }

@@

%% Ohta
{\color{blue} Next, we examine the validation of our computational method in which
we compare with the ``bubble deformation in simple linear shear flow'' 
results reported by
Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
deformation under the condition of $Re \approx 0$. In our study, using the
computational domain with $\lwh{12}{6}{6}$ and the finer grid sizes with 
(i)
$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$, and
(ii)
$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/24$, 
computations were
performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
with $Re \approx 0$ ($Re =
5.0 \times 10^{-4}$),  
$\lambda = 1.2 \times 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.
The parameters that we have prescribed are consistent with the 
experimental conditions by Muller-Fischer et al.
\cite{MulTobDreFisWin08}.  
Comparisons of our numerical results and previous
experimental results (\cite{MulTobDreFisWin08}) are tabulated in
Table~\ref{tab:DeComparisonRe=0}.  
Additionally, in
Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by Rust and
Manga (\cite{RusMan02}). These experimental values by Rust and Manga
(\cite{RusMan02}) were obtained from the graph showing the relation of $D$ vs
$Re$ (\cite{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
numerical results predicted larger values of $D$ than experimental ones
reported by Muller-Fischer et al.~\cite{MulTobDreFisWin08}. Nevertheless, we
found that our numerical results are very close to the experimental results by
Rust and Manga (\cite{RusMan02}), which emphasizes the intrinsic difficulties
associated with experimental investigations of bubble dynamics, even in simple
linear shear flow.  These comparisons suggest that our computational method is
effective and robust at reproducing bubble dynamics in simple linear shear
flow.}

%%
\begin{table}[tbh]
{\color{blue}
\caption{Comparison of  {\color{red} $D$} for a bubble as a function 
         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
	 In all cases, the domain 
         size is $\lwh{12}{6}{6}$.
         CLSVOF computations used a two-level AMR computational domain 
         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 }
\label{tab:DeComparisonRe=0}
%\footnotesize
\center
\begin{tabular}{ c  c  c  c  c }
\hline
\hline
Capillary number & 0.96  & 1.63  \\
{$D$}(Muller-Fischer et al. (\cite{MulTobDreFisWin08}))   & 0.37   &   0.58     \\
{$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.76     \\
{$D$}(Our study $\Delta x^{\ell=1}=R/24$)  & 0.63   &   0.75     \\
\hline
\hline
\end{tabular}
\end{table}
%%

%%%%
%\begin{comment} 
\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{DropBreakComparison}
  \caption{Comparison with results reported in~\cite{RenCri01-2} (shown in boxes) 
           for drop breakup in shear flow.  (The computational domain
           dimensions $W=4R$ and $H=8R$ were fixed, while $L$ was changed depending 
           on $Re$ and $Ca$ conditions, and the grid size was set to 
           $\Delta x=\Delta y=\Delta z=R/8$.  Reprinted with permission from 
           reference~\cite{RenCri01-2}. Copyright 2001, AIP Publishing). Results
           obtained with our CLSVOF algorithm, corresponding to each case in
           reference~\cite{RenCri01-2}, are shown outside boxes.  The
           CLSVOF method used a two-level AMR computational domain 
           with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
           = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
           $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$. 
           The onset of drop breakup is demonstrated for (a) $Re=10$,
           $Ca=0.16$, (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.
           For all three $Re$ and $Ca$ conditions, $\lambda = \eta = 1$.}
  \label{fig:DropBreakComp}
\end{figure}
%\end{comment} 
%

@@

\subsection{Consideration of domain and grid sizes}\label{sec:DomGrdSize}
%  -----------------------------------------------------------------------------
The computational domain size used in numerical studies can affect the behavior
of drop deformation and breakup.  Referring to
Figure~\ref{fig:SchemAndGrid}(a), with an appropriately large domain length $L$
and a fixed width $W=4R$, the effect of the height $H$ on drop behavior was
examined in~\cite{LiRenRen00} for Stokes flows and various $Ca$ conditions and
in~\cite{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.  Other related studies
investigated drop breakup sensitivity~\cite{RenCri01-1} and drop deformation
sensitivity~\cite{RenCriLi02} with respect to the entire domain size.
%
\begin{table}[tbh]
\caption{Comparison of the Taylor deformation parameter {\color{red} $D$} for a drop as a function of
         domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).
         CLSVOF method computations used a two-level AMR computational domain 
         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
\label{tab:DomComparison}
%\footnotesize
\center
\begin{tabular}{ c  c  c}
\hline
\hline
System      & Domain size ($\LWH$)         & {\color{red} $D$}    \\
System 1    & $8R  \times 4R  \times 8R$   & Breakup \\
System 2    & $12R \times 4R  \times 8R$   & Breakup \\
System 3    & $8R  \times 4R  \times 6R$   & 0.541   \\
System 4    & $8R  \times 6R  \times 6R$   & 0.466   \\
System 5    & $8R  \times 8R  \times 8R$   & 0.460   \\
System 6    & $8R  \times 16R \times 16R$  & 0.460   \\
\hline
\hline
\end{tabular}
\end{table}
%

@@

@@

%% variance for X^T X c = b
%% (S/(n-m)) (X^T X)^{-1}
%\begin{comment} 
\begin{figure}%[h!]
  \centering
  %\includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
  \includegraphics[width=\textwidth]{CaRecFit}
  \caption{A plot of the critical Reynolds number versus Capillary number
	for the data listed in Table~\ref{tab:CaRecComparison}.  
	$\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
        the initial/boundary conditions are given by (\ref{IC_BC}).
	Given a new data point, $(Ca,Re)$, one
	can reliably predict whether the 
	given $(Ca,Re)$ pair will result in shear
	induced bubble break-up or not.  
	   }
  \label{fig:CaRecFit}
\end{figure}
%\end{comment} 
%

>>>>

In this work we focus on identifying critical flow states numerically, in terms
of dimensionless quantities, that specify the extreme conditions at which a
bubble or drop in shear flow first transitions from deformation to breakup.
We validate our numerical method through comparisons with previous
shear-driven drop dynamics results and we also examine the effect of drop
deformation and breakup sensitivity on domain and grid size.  An advantage of
studying shear-driven bubble deformation and breakup computationally, rather
than experimentally, is that we can easily modify fluid physical properties to
ascertain the sensitivity of deformation and breakup to physical parameters.
In our computations, the time-evolution of the boundary between gas and liquid
is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.  
We focus on determining critical physical
conditions in which the breakup of a bubble occurs in shear flow because it is
important to identify the parameter regimes in which a relatively simple system
transitions from stable to unstable.  Specifically, we identify the critical
Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
a function of $Ca$. 
The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
reported previously by \cite{LiRenRen00}.
{\color{red} In previous studies on the motion of bubble deformation
in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low 
$Re$ number conditions ({\color{blue} $Re \ll 1$}) have been reported.}
%{\color{blue} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
In this work we determine, for the first time, the critical Reynolds number ({\color{blue} $Re \gg 1$}) 
that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
distinguish the deformation and breakup processes of a drop versus those of a bubble.

@@

When comparing with previous drop studies, we fix $\lambda=1$.  As a result,
(for $\lambda=1$) the following dimensionless physical parameters are used to
describe the problem of drop deformation/breakup in shear flow
%
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{\rm {\color{red}m}}UR}{\mu_{\rm {\color{red}m}}}, \quad
  Ca = \frac{\mu_{\rm {\color{red}m}}U}{\sigma}, \quad
  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
	\hspace{20pt} m=\mbox{matrix fluid}
\end{eqnarray}
%
$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
problem of shear-induced drop deformation and breakup, the velocity is set to
$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
mentioned in the introduction, most previous drop studies set $\eta =
1$ (e.g. \cite{LiRenRen00}).  
Thus, for comparison with previous drop deformation and breakup
problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
so that $g=0$). On the other hand, in our computations for bubble deformation,
we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$
and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize
that for consistency with previous studies (\cite{LiRenRen00, RusMan02,
MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
%{\color{blue} cite some of these previous studies which examine deformation
%and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
we computationally examine the deformation and breakup of a bubble in simple
linear shear flow as a function of the $Re$ and $Ca$ numbers.  {\color{red}
That is to say, by setting $g=0$, we are isolating the effect of only varying
$Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we
determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$
corresponds to the threshold of bubble (or drop) breakup.  We determine the
critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density
ratio and viscosity ratio. }

@@

%% Ohta
{\color{blue} Next, we examine the validation of our 
computational method in which
we compare with the ``bubble deformation in simple linear shear flow'' 
results reported by
Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
deformation under the condition of $Re \approx 0$. 
In our study, we computed
the bubble deformation on a 
computational domain with dimensions
$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid 
size was
$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
Computations were
performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  
$\lambda = 1.2 \times 10^{-3}$ and  
$\eta \leq 1.2 \times 10^{-6}$.
The parameters that we have prescribed are consistent with the 
experimental conditions by Muller-Fischer et al.
\cite{MulTobDreFisWin08}.  
Comparisons of our numerical results and previous
experimental results (\cite{MulTobDreFisWin08}) are tabulated in
Table~\ref{tab:DeComparisonRe=0}.  
Additionally, in
Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by Rust and
Manga (\cite{RusMan02}). These experimental values by Rust and Manga
(\cite{RusMan02}) were obtained from the graph showing the relation of $D$ vs
$Re$ (\cite{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
numerical results predicted larger values of $D$ than experimental ones
reported by Muller-Fischer et al.~\cite{MulTobDreFisWin08}. Nevertheless, we
found that our numerical results are very close to the experimental results by
Rust and Manga (\cite{RusMan02}), which emphasizes the intrinsic difficulties
associated with experimental investigations of bubble dynamics, even in simple
linear shear flow.  These comparisons suggest that our computational method is
effective and robust at reproducing bubble dynamics in simple linear shear
flow.}

%%
\begin{table}[tbh]
{\color{blue}
\caption{Comparison of  {\color{red} $D$} for a bubble as a function 
         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
	 In all cases, the domain 
         size is $\lwh{12}{6}{6}$.
         CLSVOF computations used a two-level AMR computational domain 
         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 }
\label{tab:DeComparisonRe=0}
%\footnotesize
\center
\begin{tabular}{ c  c  c  c  c }
\hline
\hline
Capillary number & 0.96  & 1.63  \\
{$D$}(Muller-Fischer et al. (\cite{MulTobDreFisWin08}))   & 0.37   &   0.58     \\
{$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.75     \\
% 8 months compute time.
\hline
\hline
\end{tabular}
\end{table}
%%

%%%%
%\begin{comment} 
\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{DropBreakComparison}
  \caption{Comparison with results reported 
	in~\cite{RenCri01-2} 
	(shown in boxes) 
        for drop breakup in shear flow.  
	In~\cite{RenCri01-2},
	the computational domain
        dimensions were 
	$W=4R$, $H=8R$, and $L$ was varied depending 
        on the $Re$ and $Ca$ conditions.  The
	grid size 
	in~\cite{RenCri01-2} 
	was set to 
        $\Delta x=\Delta y=\Delta z=R/8$.  
	Reprinted with permission from 
        reference~\cite{RenCri01-2}. 
	Copyright 2001, AIP Publishing. 
	Results
        obtained with our CLSVOF algorithm, corresponding to each case in
        reference~\cite{RenCri01-2}, are shown outside boxes.  The
        CLSVOF method used a two-level AMR computational domain 
        with a level-0 discretization 
	$\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$ 
	and a level-1 discretization
        $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$. 
        The onset of drop breakup is demonstrated for (a) $Re=10$,
        $Ca=0.16$, (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.
        For all three $Re$ and $Ca$ conditions, $\lambda = \eta = 1$.}
  \label{fig:DropBreakComp}
\end{figure}
%\end{comment} 
%

@@

\subsection{Consideration of domain and grid sizes}\label{sec:DomGrdSize}
%  ------------------------------------------------------------------------

\subsubsection{Selecting the appropriate domain size}

The computational domain size used in numerical studies can affect the behavior
of drop deformation and breakup.  Referring to
Figure~\ref{fig:SchemAndGrid}(a), with an appropriately large domain length $L$
and a fixed width $W=4R$, the effect of the height $H$ on drop behavior was
examined in~\cite{LiRenRen00} for Stokes flows and various $Ca$ conditions and
in~\cite{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.  Other related studies
investigated drop breakup sensitivity~\cite{RenCri01-1} and drop deformation
sensitivity~\cite{RenCriLi02} with respect to the entire domain size.
%
\begin{table}[tbh]
\caption{Comparison of the Taylor deformation parameter {\color{red} $D$} for a drop as a function of
         domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).
         CLSVOF method computations used a two-level AMR computational domain 
         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
\label{tab:DomComparison}
%\footnotesize
\center
\begin{tabular}{ c  c  c}
\hline
\hline
System      & Domain size ($\LWH$)         & {\color{red} $D$}    \\
System 1    & $8R  \times 4R  \times 8R$   & Breakup \\
System 2    & $12R \times 4R  \times 8R$   & Breakup \\
System 3    & $8R  \times 4R  \times 6R$   & 0.541   \\
System 4    & $8R  \times 6R  \times 6R$   & 0.466   \\
System 5    & $8R  \times 8R  \times 8R$   & 0.460   \\
System 6    & $8R  \times 16R \times 16R$  & 0.460   \\
\hline
\hline
\end{tabular}
\end{table}
%

@@

\subsubsection{Selecting the appropriate grid size}

{ \color{red}
The grid size and adaptive meshing strategy that we adopt is chosen
in order to answer the research question as to the conditions which determine
whether a bubble in shear flow
will break-up or not.  In such a case, we must accurately capture the 
balance of forces with respect to the (non-local) force exerted from the 
wall driven 
flow acting against the interfacial
surface tension force.  By nature of the research question, 
the accuracy of the transition
point for break-up depends intimately on the 
largest Taylor Deformation parameter $D$
that is supported by the grid (see e.g. Figures \ref{fig:ShearStress} and
\ref{fig:BubBrkCa0p8Re43}).  
As we report here, we have found that as
long as the grid size is fine enough to support a Taylor Deformation parameter
$D<0.95$, then the transition region 
(see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit}) will be captured
with a tolerance of three percent.  The simulation time becomes impractical
if we were to try to further improve the tolerance.  A smaller tolerance
would necessitate a longer supported Deformation
parameter $D$ which would in turn necessitate a higher aspect ratio
computational domain, increased droplet surface area at break-up,
increased number of time steps, and higher resolution for representing the
drop/bubble at its thinnest point.

We make the distinction between our present research, and the research found
in the work of Zang, Ni, 
and Magnaudet\cite{zhang2021three,zhang2022three} on predicting the
conditions for bubble mergers.  Even in the most extreme cases for
mergers, the largest Deformation parameter never exceeds
$0.4$ in \cite{zhang2021three}.  In summary, our gridding requirements 
necessitate grid points distributed relatively evenly throughout the 
computational domain when a bubble is stretched to a $0.9$ aspect ratio,
whereas in \cite{zhang2021three} the gridding strategy necessitates 
a localized strategy.

}

@@

%% variance for X^T X c = b
%% (S/(n-m)) (X^T X)^{-1}
%\begin{comment} 
\begin{figure}%[h!]
  \centering
  %\includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
  \includegraphics[width=\textwidth]{CaRecFit}
  \caption{A plot of the critical Reynolds number versus Capillary number
	for the data listed in Table~\ref{tab:CaRecComparison}.  
	$\lambda = 1.2 \times 10^{-3}$, 
	$\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
        the initial/boundary conditions are given by (\ref{IC_BC}).
	Given a new data point, $(Ca,Re)$, one
	can reliably predict whether the 
	given $(Ca,Re)$ pair will result in shear
	induced bubble break-up or not.  Note, for the ``Drop delineation
	curve,'' $\lambda=\eta=1$.
	   }
  \label{fig:CaRecFit}
\end{figure}
%\end{comment} 
%
